Radio Emission from Red-Giant Hot Jupiters

### 2015-09-23 ms.tex
small edits

Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}). 
%We can see emission only from where the cyclotron frequency (equation (\ref{eq:fcyc})) exceeds the plasma frequency along the line of sight:
%%%
%\begin{equation}
%\label{eq:fcyc>fplasma} \nu_{\rm cyc} > \nu_{\rm plasma}^{\rm los}
%\end{equation} 
%%%
The doubly hashed regions in Figure \ref{fig:radio} indicate the parameter spaces where the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and thus the radio emission from the planet cannot be observed from the Earth. 
In reality, the peak of the auroral radio emission does not always occur at the maximum frequency. Instead, it usually exits at lower frequencies. Here, we also consider one more criteria, $0.1 \nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ as a conservative measure for the observability of the bulk of radio emission. In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines. 
It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. 
For a red-giant system, the most promising target is massive companions with $M_p \gtrsim 5M_{\rm J}$. 
On the other hand, for a AGB-star system, only massive planets at distant orbits are marginally detectable.

@@

A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind. Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars. 
The promising targets are massive planetary ($M_p \gtrsim 5M_{\rm J}$ \memoYF{what shall we say?}) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).

>>>>

Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}). 
%We can see emission only from where the cyclotron frequency (equation (\ref{eq:fcyc})) exceeds the plasma frequency along the line of sight:
%%%
%\begin{equation}
%\label{eq:fcyc>fplasma} \nu_{\rm cyc} > \nu_{\rm plasma}^{\rm los}
%\end{equation} 
%%%
The doubly hashed regions in Figure \ref{fig:radio} indicate the parameter spaces where the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and thus the radio emission from the planet cannot be observed from the Earth. 
In reality, the peak of the auroral radio emission does not always occur at the maximum frequency. Instead, it usually exits at lower frequencies. Here, we also consider one more criteria, $0.1 \nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ as a conservative measure for the observability of the bulk of radio emission. In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines. 
It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. 
For a red-giant system, the most promising targets are massive companions with $M_p \gtrsim 4M_{\rm J}$, while the smaller ones at distant orbits are also accessible.  
% $M_p \gtrsim 4M_{\rm J}$ is well observable at 5 AU. 
On the other hand, for a AGB-star system, only very massive planets at distant orbits are marginally detectable.

@@

A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind. Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars. 
The most promising targets are massive planetary ($M_p \gtrsim 4 M_{\rm J}$ companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
